---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

> Some cats are born fat, some achieve fatness, others have fatness thrust upon them.

An [#rstats](https://twitter.com/hashtag/rstats) tribute script, in honor of the very charming [lexiross/fattest-cat](https://github.com/lexiross/fattest-cat), a script to find the fattest [cat currently up for adoption at SF SPCA](https://www.sfspca.org/adoptions/cats). Why should JavaScript have all the fun?

Incidentally, this makes a pretty good demo of using the [tidyverse](https://blog.rstudio.org/2016/09/15/tidyverse-1-0-0/) to work in a style I call [Data Rectangling](https://speakerdeck.com/jennybc/data-rectangling).

## Install and call

From a shell

```
wget https://raw.githubusercontent.com/jennybc/fattest-cat/master/fattest-cat.R
chmod +x fattest-cat.R
./fattest-cat.R
```

From R

```{r eval = FALSE}
url <- "https://raw.githubusercontent.com/jennybc/fattest-cat/master/fattest-cat.R"
rfile <- basename(url)
download.file(url, rfile)
source(rfile)
```

## Demo

```{sh, cache = TRUE}
./fattest-cat.R
```
